---
output: github_document
---
<!-- README.md is generated from README.Rmd. Please edit that file -->


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# glosario

<!-- badges: start -->
[![R build status](https://github.com/carpentries/glosario-r/workflows/R-CMD-check/badge.svg)](https://github.com/carpentries/glosario-r/actions)
[![codecov](https://codecov.io/gh/carpentries/glosario-r/branch/master/graph/badge.svg)](https://codecov.io/gh/carpentries/glosario-r)
<!-- badges: end -->

`glosario` allows users to create and retrieve multilingual glossaries. By
default, `glosario` provides access to a [community-curated glossary](https://github.com/carpentries/glosario) hosted by The Carpentries. This repository also documents the structure expected for the glossaries that can be managed by `glosario`. 

There is also a [Python interface](https://glosario.readthedocs.io/en/latest/).

## Installation

`glosario` is still in the development stage and is only available from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("carpentries/glosario-r")
```
## Example


```{r example}
library(glosario)
g <- get_glossary()
g
define("slug", glossary = g)
```

To get definitions in other languages we would do:

```{r french}
g <- get_glossary()
define("plus_one", lang = 'fr', glossary = g)
```
