---
title: "Basic Usage"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Basic Usage}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

To get a single definition, you just need to pass a slug with the term you want defined.

```{r setup}
library(glosario)

define('data_frame')
```

If you don't know the exact slug for the term you're searching, don't worry. Type the term as close as you remember and `define` will try to match it to the closes term we have available.

```{r}
define('data frame')
```

`define` is not constrained to a single language. In one code chunk you can define terms both in English and French, for example.

```{r}
define('plus one', lang = 'en')
define('plus one', lang = 'fr')
```

If you want to use your custom glossary file you can do it the following way:

```{r}
custom_url <- "https://raw.githubusercontent.com/carpentries/glosario/master/glossary.yml"

g <- get_glossary(url = custom_url)

define("plus_one", lang = 'fr', glossary = g)
```
