---
title: "RMarkdown Support"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{rmd_support}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(glosario)
```

To add links to definitions, you can use the `gdef` function for inline writing:

```{r, eval=FALSE}
This is a `r gdef('data_frame', 'Data Frame')`, they are used for storing data.
```

Which would look like this:

> This is a `r gdef('data_frame', 'Data Frame')`, they are used for storing data.

The `gdef` function depends on the YAML header being set up under the `glosario` key. An example of a YAML header for glosario would be: 

```YAML
title: "Test Glosario RMD Support"
output: html_document
glosario:
  base_url:
    - https://glosario.carpentries.org
  language:
    - en
  requires:
  - readr
  defines:
  - data_frame
```

An explanation of the keys follows:

| Key | Explanation |
|:---:|:-----------:|
|`base_url`| URL where the links will point to|
|`language`| Language of the terms|
|`requires`| Terms that have to be known before starting the lesson|
|`defines`| The terms that are defined in this lesson |
